Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-01-06 supplement.tex
update figures

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/supp-relate-rccr-data}
    \caption{
        \textbf{Relative cross-coalescence rates inferred from the data.}
    }
    \label{fig:supp-rccr-data}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/supp-relate-iicr-data-full-and-subset}
    \caption{
        \textbf{Inverse instantaneous coalescence rates inferred from the data,
        subset to focal populations in the model inferences.}
    }
    \label{fig:supp-iicr-data-subset}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/supp-relate-rccr-data-full-and-subset}
    \caption{
        \textbf{Relative cross-coalescence rates inferred from the data.}
    }
    \label{fig:supp-rccr-data}
\end{figure}
